### 2019-08-23 Manuscript/Manuscript.tex
Updates from Overleaf

% details of DynSoil and GEOCLIM
% details of parameter exploration/calibration
    % basin data used for parameter exploration
% details of lithology implementation

@@

The broader Indonesia Archipelago has an out-sized influence on modern chemical weathering fluxes. The confluence of steep topography, a warm and wet tropical climate, and the presence of mafic lithologies results in high fluxes of Ca and Mg cations and associated \COtwo consumption \citep{Hartmann2009a, Hartmann2014a}. There has been significant growth of land area within the region since the Miocene associated with ongoing arc-continent collision between Australia and the Sunda-Banda arc system (\citealp{Molnar2015a}; Fig. \ref{Fig:indo_growth}). This collision between the Australian-Indian and Eurasian plates and intervening arc terranes has led to the emergence of Indonesia and New Guinea and the exhumation of large supra-subduction ophiolites and associated forearcs in the warm, wet tropics.

@@

Of the various parameters used in the equations that govern the silicate weathering component of GEOCLIM (see SI), four parameters in particular are poorly constrained in the existing literature: the proportionality constant that modifies the dependence of dissolution rate on runoff and temperature ($k_{d}$), the proportionality constant that modifies the dependence of dissolution rate on runoff only ($k_{w}$), the power constant that modifies the dependence of dissolution rate on the time that a rock particle has spent in the regolith ($\sigma$), and the proportionality constant that modifies the dependence of regolith production on runoff and temperature ($k_{rp}$). As discussed above, the Ca+Mg concentrations of metamorphic and siliciclastic sediment grid cells are also difficult to define. Rather than prescribing values for these six parameters, we instead allowed these parameters to vary within reasonable bounds, resulting in a total of 78,000 unique parameter combinations. For each of these combinations, we computed spatially-resolved long-term \COtwo consumption (i.e. Ca+Mg consumption) using present-day runoff, temperature, and slope fields. Following the approach of \citet{Maffre2018a}, we then summed the computed \COtwo consumption over large-scale watersheds that appear in the global compilation of \citet{Gaillardet1999a} as well as smaller-scale watersheds of the Amazon Basin in the compilation of \citet{Moquet2011a, Moquet2016a, Moquet2018a}, then calculated the coefficient of determination ($r^{2}$) between computed and measured \COtwo consumption in each of these basins. Finally, we eliminate all parameter combinations that result in unreasonable total global \COtwo consumption (which we define to be \textless1\times10$^{12}$~mol/yr or \textgreater1\times10$^{13}$~mol/yr) and/or result in a low $r^{2}$ (which we define to be \textless0.4). This calibration method leaves 3,339 unique parameter combinations that produce total global and individual watershed \COtwo consumption fluxes that approximate those estimated in the literature for the present day.

@@

We use geological and paleoshoreline data to quantify the changes in the area of the broader Indonesia Archipelago over the past 20~m.y. Following \citet{Molnar2015a}, we analyzed the area changes of islands that are greater than $\sim$200~km, and we also included changes in areas of submerged continental shelves that were previously exposed, like the Sunda Shelf. Carbonate strata and thin-bedded siliciclastic strata were interpreted to represent a subaqueous marine environment, whereas evidence for exposure and terrestrial siliciclastic deposits were used as evidence for a subaerial environment. Taken together, these constraints delineate the position of shorelines. For the island of Sulawesi, we followed the recent stratigraphic compilation and paleoshorelines delineated by \citet{Nugraha2018a} and for New Guinea we followed work of \citet{Norvick2003a, Cloos2005a, Gold2017a}. While there are difference in data sources and paleoshoreline outlines from \cite{Molnar2015a}, the calculated area at 5~Ma is quite similar.

@@

Given these uncertainties, we test three scenarios related to the growth of the Indonesia Archipelago. The "removed Indonesia Archipelago" represents an end-member scenario, in which all islands associated with

We incorporate land area associated with the subsided Sunda Shelf into our modeling.

@@

\begin{figure}
    \centering
    \includegraphics{Manuscript/Figures/shoreline_growth.pdf}
    \caption{Growth of the broader Indonesia Archipelago. Past shorelines are shown in A with resultant area estimates summarized in B. A significant increase in area over the past 5 million years is coincident with cooling and the onset of Northern Hemisphere glaciation as reflected in the benthic oxygen isotope record in C \cite{Zachos2008a}.}
    \label{fig:shoreline_growth}
\end{figure}

>>>>

% details of DynSoil and GEOCLIM
% details of parameter exploration/calibration
    % basin data used for parameter exploration
% details of lithology implementation
    % including Sunda Shelf

@@

The broader Indonesia Archipelago has an out-sized influence on modern chemical weathering fluxes. The confluence of steep topography, a warm and wet tropical climate, and the presence of mafic lithologies results in high fluxes of Ca and Mg cations and associated \COtwo consumption \citep{Hartmann2009a, Hartmann2014a}. There has been significant growth of land area within the region since the Miocene associated with ongoing arc-continent collision between Australia and the Sunda-Banda arc system (\citealp{Molnar2015a}; Fig. \ref{fig:shoreline_growth}). This collision between the Australian-Indian and Eurasian plates and intervening arc terranes has led to the emergence of Indonesia and New Guinea and the exhumation of large supra-subduction ophiolites and associated forearcs in the warm, wet tropics.

@@

Of the various parameters used in the equations that govern the silicate weathering component of GEOCLIM (see SI), four parameters in particular are poorly constrained in the existing literature: the proportionality constant that modifies the dependence of dissolution rate on runoff and temperature ($k_{d}$), the proportionality constant that modifies the dependence of dissolution rate on runoff only ($k_{w}$), the power constant that modifies the dependence of dissolution rate on the time that a rock particle has spent in the regolith ($\sigma$), and the proportionality constant that modifies the dependence of regolith production on runoff and temperature ($k_{rp}$). As discussed above, the Ca+Mg concentrations of metamorphic and siliciclastic sediment grid cells are also difficult to define. Rather than prescribing values for these six parameters, we instead allowed these parameters to vary within reasonable bounds, resulting in a total of 78,000 unique parameter combinations. For each of these combinations, we computed spatially-resolved long-term \COtwo consumption (i.e. Ca+Mg consumption) using present-day runoff, temperature, and slope fields. Following the approach of \citet{Maffre2018a}, we then summed the computed \COtwo consumption over large-scale watersheds that appear in the global compilation of \citet{Gaillardet1999a} as well as smaller-scale watersheds of the Amazon Basin in the compilation of \citet{Moquet2011a, Moquet2016a, Moquet2018a}, then calculated the coefficient of determination ($r^{2}$) between computed and measured \COtwo consumption in each of these basins. Finally, we eliminate all parameter combinations that result in unreasonable total global \COtwo consumption (which we define to be \textless1\times10$^{12}$~mol/yr or \textgreater1\times10$^{13}$~mol/yr) and/or result in a low $r^{2}$ (which we define to be \textless0.4). This calibration method leaves 3,339 unique parameter combinations that produce global and individual watershed \COtwo consumption fluxes that approximate those estimated in the literature for the present day.

@@

We use geological and paleoshoreline data to quantify the changes in the area of the broader Indonesia Archipelago over the past 20~m.y (Fig. \ref{fig:shoreline_growth}). Following \citet{Molnar2015a}, we analyzed the area changes of islands that are greater than $\sim$200~km, and we also included changes in areas of submerged continental shelves that were previously exposed, like the Sunda Shelf. Carbonate strata and thin-bedded siliciclastic strata were interpreted to represent a subaqueous marine environment, whereas evidence for exposure and terrestrial siliciclastic deposits were used as evidence for a subaerial environment. Taken together, these constraints delineate the position of shorelines. For the island of Sulawesi, we followed the recent stratigraphic compilation and paleoshorelines delineated by \citet{Nugraha2018a} and for New Guinea we followed work of \citet{Norvick2003a, Cloos2005a, Gold2017a}. While there are difference in data sources and paleoshoreline outlines from \cite{Molnar2015a}, the calculated area at 5~Ma is quite similar.

@@

Given these uncertainties, we test three scenarios related to the growth of the Indonesia Archipelago (Fig. \ref{fig:scenario_pCO2}). The "removed Indonesia Archipelago" scenario represents an end-member scenario, in which all islands associated with arc-continent collision in the area are entirely removed. The "reduced Indonesia Archipelago" scenario represents our best estimate of the subaerial extent of islands in the area at ca. 15~Ma, excluding the Sunda Shelf. The "reduced Indonesia Archipelago + Sunda Shelf" is identical to the "reduced Indonesia Archipelago" scenario with the addition of the Sunda Shelf. Given that no land in the Sunda Shelf is currently exposed, across the shelf we distribute felsic and siliciclastic lithologies, assign shallow slope values, and interpolate runoff across latitude bands (see SI).

Our results indicate that

@@

\begin{figure}
    \centering
    \includegraphics[width=1\textwidth]{Manuscript/Figures/shoreline_growth.pdf}
    \caption{Growth of the broader Indonesia Archipelago. Past shorelines are shown in A with resultant area estimates summarized in B. A significant increase in area over the past 5 million years is coincident with cooling and the onset of Northern Hemisphere glaciation as reflected in the benthic oxygen isotope record in C \cite{Zachos2008a}.}
    \label{fig:shoreline_growth}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=1\textwidth]{Manuscript/Figures/shoreline_growth.pdf}
    \caption{Placeholder for steady state pCO2 figure.}
    \label{fig:scenario_pCO2}
\end{figure}
